PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-03-29 refereeResponse.txt

394: small alpha, large beta doesn't look dynamically cool to me.
	This should have been referring to the dynamical state of the growing protoplanets, relative to the initial eccentricities of the planetesimals. This has now been clarified in the text.
400: Small alpha large beta does not look dynamically cooler than large alpha large beta to me. In fact, the opposite.
	You are correct! This is a mistake in the text (replaced 'latter' with 'former').
402: I don't really understand why small alpha small beta leads to so many dynamically hot bodies, both planetesimals and protoplanets. Maybe the authors can elaborate.
	When alpha and beta are both small, the gravitational stirring timescale is very short and the disk quickly heats up. Because the stirring timescale goes as v^{1/4} (TODO: reference), the scattering slows down as the disk gets hotter. So runaway growth doesn't really kick in until after the eccentricities have grown enough that stirring slows down. I think this is why the initial choice of beta doesn't really seem to affect the final dynamical state of the disk in figure 2. This is also why the initial choice of e_h isn't very consistent across planetesimal accretion studies (cite some examples). TODO: Let's add another paragraph discussing this here.

Figure 3:
Again, I really think labeling the cases would be helpful.
I would express the mass in units of e.g. Ceres
	Todo: Push back on this? Use dimensionless units for this section.
406: I'm not sure about "significantly" larger. The biggest body in large alpha, small beta is about a factor 3 more massive than in small alpha, small beta. This is only a factor of 1.4 in size.
	The text now says 'a factor of a few larger'
415: the y-label in Fig.6 does not match the description in the text
	This comment must be referring to figure 4? If so, 'm_max' in the text has been changed to 'M'.
Figure 4:
Why don't the simulations start all with m_max/m = 1?
I'd be interested in also having another panel that shows the evolution of just M_max and <m> (maybe in solid and dashed lines) for the four simulations. That would also underscore that the turnover is driven by an increase in <m> rather than m_max.
	We have now added a second panel to figure 4 which shows the evolution of these quantities separately. Todo: Units? Why does the max mass decrease for case a?

### 2023-03-29 main.tex
Referee changes through update to fig 4

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
    \caption{The evolution of the ratio between the maximum and mean mass for the four simulations presented in section 
    \ref{sec:narrow}. The runaway growth phase can be identified by a positive trend in this ratio. For all values of $\alpha$, an 
    increase in $\beta$ has the effect of delaying runaway growth.\label{fig:alpha_beta_evo}}
\end{center}
\end{figure}

@@

In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}. In addition to leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce significantly larger embryos. Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) appears to have no significant effect on the final distribution of masses.

To investigate whether any of these planetesimal rings underwent
runaway growth, we examine the time evolution of the maximum and mean
masses in each simulation. The ratio $m_{max}/\left< m \right>$ is plotted
in figure \ref{fig:alpha_beta_evo}. On this plot, a positive slope
indicates that the quantities are diverging (i.e.
the growth rate is accelerating with mass). This behavior is
evident in all four cases. Even with a large
$\beta$, where the effective collision cross section is
 nearly equal to the geometric value, runaway growth still appears to
operate. The ubiquity of the early positive trends in this figure suggests
that as bodies collide and grow, the
relative difference in gravitational focusing factors between bodies
is what drives the system towards runaway
growth, no matter how close the collision cross sections lie to the geometric value.
Although larger encounter velocities lengthen the growth
timescales, runaway growth appears to be inevitable, so long as
gravity is the dominant force in the system. For large $\alpha$
\textbf{(case a, b)}, the curves in this figure eventually turn over and begin to decline.
Upon inspecting the simulation snapshots, we find that this trend is
driven by an increase in the average mass as the planetesimal population
becomes depleted. One should expect that the same thing will eventually
occur for small $\alpha$, although many more timesteps are required to
begin to run out of planetesimals.

>>>>

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/alpha_beta_evo.png}
    \caption{\textbf{Top:} The evolution of the ratio between the maximum and mean mass for the four simulations presented
    in section \ref{sec:narrow}. The runaway growth phase can be identified by a positive trend in this ratio. For all values of 
    $\alpha$, an increase in $\beta$ has the effect of delaying runaway growth. \textbf{Bottom: The evolution of the maximum
    (solid lines) and mean (dashed lines) shown individually.}\label{fig:alpha_beta_evo}}
\end{center}
\end{figure}

@@

In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}. In addition to leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce \textbf{embryos that are a factor of a few larger}. Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) appears to have no significant effect on the final distribution of masses.

To investigate whether any of these planetesimal rings underwent
runaway growth, we examine the time evolution of the maximum and mean
masses in each simulation. The ratio $M/\left< m \right>$ is plotted
in \textbf{the top panel of} figure \ref{fig:alpha_beta_evo}. \textbf{Here}, a positive slope
indicates that the quantities are diverging (i.e.
the growth rate is accelerating with mass). This behavior is
evident in all four cases. Even with a large
$\beta$, where the effective collision cross section is
 nearly equal to the geometric value, runaway growth still appears to
operate. The ubiquity of the early positive trends in this figure suggests
that as bodies collide and grow, the
relative difference in gravitational focusing factors between bodies
is what drives the system towards runaway
growth, no matter how close the collision cross sections lie to the geometric value.
Although larger encounter velocities lengthen the growth
timescales, runaway growth appears to be inevitable, so long as
gravity is the dominant force in the system. For large $\alpha$
\textbf{(case a, b)}, the curves in this figure eventually turn over and begin to decline.
\textbf{In the bottom panel of figure \ref{fig:alpha_beta_evo}, we separately show the evolution of
the maximum (solid lines) and mean (dashed lines) mass for each case. Here, it is evident}
that \textbf{the turnover in $M/\left< m \right>$} is
driven by an increase in the average mass as the planetesimal population
becomes depleted. One should expect that the same thing will eventually
occur for small $\alpha$, although many more timesteps are required to
begin to run out of planetesimals.
